Title

### 2023-09-27 main.tex
fig 4 y 8

{\color{green}
\begin{figure} % {{{
\centering
\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
\caption{
{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
The implementation was done on IBM's ibmq-lima quantum computer.
Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
doesn't considerably affect fidelity.}
\label{fid} 
\end{figure} % }}}
}

>>>>

{\color{green}
\begin{figure} % {{{
\centering
\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
\caption{
{\bf Fidelities for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
The implementation was done on IBM's ibmq-lima quantum computer.
Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
doesn't considerably affect fidelity.}
\label{fid} 
\end{figure} % }}}
}
